Composing like a human

### 2019-05-10 paper/images/c_rnn_gan/c_rnn_gan_1_5bach-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5-acts-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5bach-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/c_rnn_gan/c_rnn_gan_1_5beethoven-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5bach-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5beethoven-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/c_rnn_gan/c_rnn_gan_1_5chopin-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5beethoven-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5chopin-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/c_rnn_gan/c_rnn_gan_1_5debussy-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5chopin-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5debussy-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/c_rnn_gan/c_rnn_gan_1_5enescu-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5debussy-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=349.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=349.5, ymax=-0.5] {images/c_rnn_gan/c_rnn_gan_1_5enescu-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5-acts.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5-acts--000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5-acts-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5bach-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5-acts-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5bach-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5bach.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5-acts-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5bach-001.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5beethoven-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5bach-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5beethoven-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5beethoven.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5bach-001.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5beethoven-001.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5chopin-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5beethoven-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5chopin-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5chopin.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5beethoven-001.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5chopin-001.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5debussy-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5chopin-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5debussy-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5debussy.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5chopin-001.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5debussy-001.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5enescu-transposed.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5debussy-transposed-000.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Events Sequences},
xmin=-0.5, xmax=199.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Activations},
ymin=-0.5, ymax=511.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=199.5, ymin=511.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5enescu-transposed-000.png};
\end{axis}

### 2019-05-10 paper/images/performance_rnn/performance_rnn_1_5enescu.tex
first draft done and added baseline_50

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5debussy-001.png};
\end{axis}

>>>>

\begin{axis}[
height=\heatheight,
tick align=outside,
tick pos=left,
width=\heatwidth,
x grid style={white!69.01960784313725!black},
xlabel={Activations},
xmin=-0.5, xmax=511.5,
xtick style={color=black},
y grid style={white!69.01960784313725!black},
ylabel={Events Sequences},
ymin=-0.5, ymax=199.5,
ytick style={color=black}
]
\addplot graphics [includegraphics cmd=\pgfimage,xmin=-0.5, xmax=511.5, ymin=199.5, ymax=-0.5] {images/performance_rnn/performance_rnn_1_5enescu-001.png};
\end{axis}
